### 2020-06-05 survival.tex
lustre heat?

In addition to the strong {\em cage} and {\em node} hazard rate
differences that increase with distance from the bottom of the
cabines, seen in both KM and CPH results, there is a weaker but
peculiar pattern in the {\em row} and {\em col} hazard rates. The
different behavior in {\em col} 0-11 from {\em col} 12-24 is likely
\rev{due to the presence of the file system to the right of {\em col}
  24, as can be seen in the floor layout of Fig.~\ref{fig:layout}. An
  explanation due to separate supply lines of chilled water to the two
  sets is not likely as the evaporators (see Fig.~\ref{fig:layout})
  are thermostat controlled.}

>>>>

In addition to the strong {\em cage} and {\em node} hazard rate
differences that increase with distance from the bottom of the
cabines, seen in both KM and CPH results, there is a weaker but
peculiar pattern in the {\em row} and {\em col} hazard rates. The
different behavior in {\em col} 0-11 from {\em col} 12-24 is likely
\rev{due to the presence of the file system to the right of {\em col}
  24, as can be seen in the floor layout of Fig.~\ref{fig:layout}. An
  explanation due to separate supply lines of chilled water to the two
  sets is not likely as the evaporators (see Fig.~\ref{fig:layout})
  are thermostat controlled.} \fix{The file system, however. did not
  have evaporator heat exchangers and relied on ambient room air for
  heat transport, affecting room temperature on the right side of
  Titan. !!Do we have room temp measurement data?!!}
